% jgerity_CV.tex
% requires the 'resume' package
% https://www.ctan.org/pkg/res 

\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{James Gerity\\[12pt]} % the \\[12pt] adds a blank line after name

\address{Department of Physics \& Astronomy \\
		Texas A\&M University \\
		College Station, TX 77843}
\address{}
                                             
\begin{resume}
                                               
 
\section{EDUCATION} 
\textbf{\noindent University of Maryland, Baltimore County (UMBC), Baltimore, MD} \\
B.S. Physics, May 2011 \\
B.S. Mathematics, May 2011

\textbf{\noindent Texas A\&M University} \\
Ph.D. Physics, In progress
 
\section{PUBLICATIONS} 
 
\begin{itemize}

\item 	J. Gerity, P. M. McIntyre, "A cooling storage ring for an electron-ion collider," in COOL 2015, Newport News, VA, 2015.
\item 	P. M. McIntyre et al., "Fixed-energy cooling and stacking for an electron ion collider," in IPAC 2015, Richmond, VA, 2015.
\item 	S. Assadi et al., "Magnet design and synchrotron damping considerations for a 100 TeV hadron collider," in IPAC 2015, Richmond, VA, 2015.
\item 	S. Assadi et al., "Higgs factory and 100 TeV hadron collider: Opportunity for a new world laboratory within a decade," arXiv preprint arXiv:1402.5973, 2014.
\item 	A. Sattarov et al., "Neutronics of accelerator-driven subcritical fission for burning transuranics in used nuclear fuel," AIP Conference Proceedings, vol. 1525, no. 1, pp. 245-250, 2013.
\item 	E. Sooby et al., "Molten salt considerations for accelerator-driven subcritical fission to close the nuclear fuel cycle," AIP Conference Proceedings, vol. 1525, no. 1, pp. 230-235, 2013.
\item 	P. McIntyre et al., "Accelerator-driven subcritical fission in molten salt core: Closing the nuclear fuel cycle for green nuclear energy," AIP Conference Proceedings, vol. 1525, no. 1, pp. 636-642, 2013.

\end{itemize}
 
\section{RESEARCH INTERESTS}
\begin{itemize}
\item Electron cooling dynamics and cooler design in regimes of strong magnetization and/or neutralization
\item Use of genetic algorithms for multi-objective optimization problems in magnet design
\item Design of 16+ T dipole magnets for FCC and other high-field applications
\item Design of 2-5 T dipole magnets for moderate-field hadron collider applications
\item Coupled simulation of heat flow and neutronics for accelerator-driven fission stability analysis
\end{itemize}
 
\section{SKILLS}
\begin{itemize}
\item Finite element simulation with multiple codes: COMSOL Multiphysics, FEniCS
\item Programming in C++ (ROOT), Python (numpy, matplotlib), Javascript (d3.js, jQuery, three.js), R
\item CAD Layout using Autodesk Inventor
\end{itemize}

\end{resume}
\end{document}
